Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-23 paper/egpaper_for_review.tex
nativ multicuts without a gm
fixed nasty bug
up paper
tables and plots
add anytime plots

\usepackage{eso-pic}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}

@@

@@

To generate proposals cut we can use bottom up hierarchical clustering.
In each step we contract the edge with the highest weight.
Parallel edges are merged into single edges by summing their weights.
We stop when a certain number of nodes is reached, or the
largest edge weight is smaller then a certain threshold.
To get versatile proposals we either add noise 
to the edge weighs or permute a certain number of weights.

@@

\section{Experiments}
\subsection{Benchmark Models}
\subsection{Pixel-wise Multicuts}
\input{inputs/fig_pixel_mc.tex}

>>>>

\usepackage{eso-pic}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage{booktabs}

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
\usepackage{dirtytalk}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usetikzlibrary{calc, matrix, backgrounds}

\pgfplotsset{every axis/.append style={
  every axis y label/.style = {at={(ticklabel cs:0.5)}, rotate=90, anchor=south},
  axis x line = {bottom},
  axis y line = {left},
  tick align = outside,
  ymajorgrids = true,
%  legend style = {draw=none, at={(1.05, 0.5)}, anchor=west, font=\small},
  legend style = {font=\tiny},
  legend columns = 1,
  every axis plot/.append style = {line width=1pt},
  label style = {font=\small},
  tick label style={font=\small},
  scaled ticks = false,
}}

\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}

@@

\def\arraystretch{0.8}
\renewcommand{\tabcolsep}{2pt}
\newcommand{\thickline}{2pt}
\newcommand{\scatterplotpath}{./scatterplots/}

@@

To generate proposals cut we can use bottom up hierarchical clustering.
In each step we contract the edge with the highest weight.
Parallel edges are merged into single edges by summing their weights.
We stop when a certain number of nodes is reached, or the
largest edge weight among the not yet contracted edges is smaller then a certain threshold.
To get versatile proposals we either add noise 
to the edge weighs or permute a certain number of weights.

@@

\section{Experiments}
\subsection{Benchmark Models}

\input{tables/anytime/image-seg.tex}

\input{tables/anytime/knott-3d-150.tex}

\input{tables/knott-3d-300.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-6000:-4500,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
%\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-150.data};
%\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-150.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-150.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-150.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-150.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-150}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-40000:-24000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-300.data};
\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-300.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-300.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-300.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-300.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-300}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-80000:-60000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-450.data};
\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-450.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-450.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-450.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-450.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-450}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
restrict y to domain=-10000000:-100000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/knott-3d-550.data};
\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/knott-3d-550.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/knott-3d-550.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC-CGC]{data/knott-3d-550.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/knott-3d-550.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{knott-3d-550}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\begin{figure}[H]
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{semilogxaxis}[
%restrict y to domain=-10000000:-100000,
xlabel = {runtime},
xmin = 0,
xmax = 4100,
%ymin =  75282844.25,
%ymax =  81774642.015,
%xtick       = { 1 , 60 , 3600 },
%xticklabels = { 1 sec. , 1 min.  , 1 hour },
%ytick       = {75661636, 78718140, 81774643 },
%yticklabels = {$75661636$, $78718140$, $81774643$ },
width = 0.9\columnwidth,
scaled ticks = false
]
\addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data/seg-3d.data};
\addlegendentry{HC-CGC}

\addplot[color=red,mark=x] table[x=time,y=CGC]{data/seg-3d.data};
\addlegendentry{CGC}

\addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data/seg-3d.data};
\addlegendentry{MCI-CCIFD}

\addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC-CGC]{data/seg-3d.data};
\addlegendentry{MC-Fusion (HC-MC-CGC)}

\addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC-CGC]{data/seg-3d.data};
\addlegendentry{MC-Fusion (HC-CGC-CGC)}

\end{semilogxaxis}
\end{tikzpicture}
\caption{seg-3d}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{tables/anytime/knott-3d-450.tex}
\begin{figure*}
\input{scatterplots/knott-3d-450.tex}
\end{figure*}

\input{tables/knott-3d-550.tex}

\input{tables/anytime/seg-3d.tex}

\input{tables/modularity-clustering.tex}

\subsection{Pixel-wise Multicuts}
\input{inputs/fig_pixel_mc.tex}
